
####Exercises - Part 1

#####1. Fix each of the following common data frame subsetting errors.

Ans:
```{r, results="hide"}
# mtcars[mtcars$cyl = 4, ]
mtcars[mtcars$cyl == 4, ]

# mtcars[-1:4, ]
mtcars[-c(1:4), ]

# mtcars[mtcars$cyl <= 5]
mtcars[mtcars$cyl <= 5, ]

# mtcars[mtcars$cyl == 4 | 6, ]
mtcars[mtcars$cyl %in% c(4, 6), ]
```


#####2. Why does `x <- 1:5; x[NA]` yield five missing values? (Hint: why is it different from `x[NA_real_]`?)

Ans: NA is a logical vector of lenggth one, thus, it is recycled to the length of x.



#####3. What does upper.tri() return? How does subsetting a matrix with it work? Do we need any additional subsetting rules to describe its behaviour?
```{r}
x <- outer(1:5, 1:5, FUN = "*")
x[upper.tri(x)]
```

Ans: It returns `TRUE` in the upper triangle of the matrix so subsetting with it returns the values in the upper triangle, column by column.


#####4. Why does `mtcars[1:20]` return an error? How does it differ from the similar `mtcars[1:20, ]`?

Ans: Because `mtcars` is a data.frame, you have to tell it which columes to select.


#####5. Implement your own function that extracts the diagonal entries from a matrix (it should behave like diag(x) where x is a matrix).

Ans:
```{r}
fn_diag <- function(x) {
  stopifnot(is.matrix(x), nrow(x) == ncol(x))
  n <- nrow(x)
  return(x[matrix(seq_len(n), nrow = n, ncol = 2)])
}
```


#####6. What does `df[is.na(df)] <- 0` do? How does it work?

Ans:
It sets NA values in df to 0.


#
####Exercises - Part 2

#####1. Given a linear model, e.g., `mod <- lm(mpg ~ wt, data = mtcars)`, extract the residual degrees of freedom. Extract the R squared from the model summary (summary(mod))

Ans:

mod$df.residual

summary(mod)$r.squared


#
####Exercises - Part 3

#####1. How would you randomly permute the columns of a data frame? (This is an important technique in random forests.) Can you simultaneously permute the rows and columns in one step?

Ans:

```{r}
(df <- data.frame(matrix(1:25, ncol = 5)))

fn_permute <- function(x) {
  nr <- nrow(x)
  nc <- ncol(x)
  x[] <- x[, sample(nc)]
  return (x)
}

# permute df
df[sample(nrow(df)), sample(ncol(df))]
```


#####2. How would you select a random sample of m rows from a data frame? What if the sample had to be contiguous (i.e., with an initial row, a final row, and every row in between)?

Ans:
```{r}
fn_random_rows <- function(df, m) {
  df[sample(nrow(df), size = m), ]
}

fn_random_rows(df, m = 3)
```

If the sample had to be contiguous:
```{r}
fn_sample_contig_rows <- function(df) {
  row_nums <- sample(nrow(df), size = 2)
  df[min(row_nums):max(row_nums), ]
}

fn_sample_contig_rows(df)
```


#####3. How could you put the columns in a data frame in alphabetical order?

Ans:
`df[, order(names(df))]`
