
#
#### Exercise - Condition handling 

#####1. Compare the following two implementations of message2error(). What is the main advantage of withCallingHandlers() in this scenario? (Hint: look carefully at the traceback.)
```{r}
message2error1 <- function(code) {
  withCallingHandlers(code, message = function(e) stop(e))
}

message2error2 <- function(code) {
  tryCatch(code, message = function(e) stop(e))
}

#message2error1(hello)
#traceback()

#message2error2(message(hello))
#traceback()
```

Ans: `withCallingHandlers()` goes into the function to show you the message that came with the function that had errors.



#
#
#### Exercise - Defensive programming

#####1. 
```{r, eval=FALSE}
data(mtcars)

col_means <- function(df) {
  numeric <- sapply(df, is.numeric)
  numeric_cols <- df[, numeric]
  data.frame(lapply(numeric_cols, mean))
}

# works fine
col_means(mtcars)

# can't take 0th column
col_means(mtcars[, 0])

# works, but mtcars[0, ] empty data frame
col_means(mtcars[0, ])

# doesn't calculate the column mean of "mpg"
col_means(mtcars[, "mpg", drop = F])

# doesn't work on vector
col_means(1:10)

# doesn't work on matrix
col_means(as.matrix(mtcars))

# doesn't work on list
col_means(as.list(mtcars))

# doesn't work on character variables
mtcars2 <- mtcars
mtcars2[-1] <- lapply(mtcars2[-1], as.character)
col_means(mtcars2)
```

Fix the `col_mean()`:
```{r, error=TRUE}
data(mtcars)

col_means <- function(df) {
  df <- data.frame(df)
  if (identical(sum(vapply(df, is.numeric, numeric(1))), 0)) stop("Not numeric values")
  else if (identical(nrow(df), as.integer(0))) stop("Empty data frame")
  else {
    numeric_cols <- df[vapply(df, is.numeric, logical(1))]
    apply(numeric_cols, 2, mean)
  }
}

col_means(mtcars) # ok
col_means(mtcars[, 0]) # ok
col_means(mtcars[0, ]) #ok
col_means(mtcars[, "mpg", drop = F]) # fixed
col_means(1:10) # fixed
col_means(as.matrix(mtcars)) # fixed
col_means(as.list(mtcars)) # fixed

mtcars2 <- mtcars
mtcars2[-1] <- lapply(mtcars2[-1], as.character)
col_means(mtcars2) # fixed
```

