
####Exercises - Function components

#####1. What function allows you to tell if an object is a function? What function allows you to tell if a function is a primitive function?

Ans: `is.function` tells if an object is a function. `is.primitive` tells if a function is a primitive function.


#####2. This code makes a list of all functions in the base package.
```{r}
objs <- mget(ls("package:base"), inherits = TRUE)
funs <- Filter(is.function, objs)
```
#####Use it to answer the following questions:
#
#####a. Which base function has the most arguments?
```{r}
require(plyr)
objs <- mget(ls("package:base"), inherits = TRUE)
funs <- Filter(is.function, objs)


# create a vector of lengths
arg_length <- lapply(funs, function(x)(length(formals(x))))
arg_length <- unlist(arg_length)

names(arg_length[arg_length == max(arg_length)])
```

`scan` has the most arguments in the base.


#
#####b. How many base functions have no arguments? What’s special about those functions?
```{r}
length(which(arg_length == 0))
```
225 base functions have no arguments.


#
#####c. How could you adapt the code to find all primitive functions?
```{r}
prims <- Filter(is.primitive, objs)
names(prims)
```


#####3. What are the three important components of a function?

Ans: The three important components of a function are: the arguments, the function content, and the environment where the variables are stored.


#####4. When does printing a function not show what environment it was created in?

Ans: if it is a primitive function.


#
#### Exercises - Lexical scoping

#####1. What does the following code return? Why? What does each of the three c’s mean?
```{r}
c <- 10
c(c = c)
```

Ans: The above performs a combine function (first c) to create a vector with an item named c (second c) with value 10 (third c).


#####2. What are the four principles that govern how R looks for values?

Ans: Name masking, functions vs. variables, a fresh start, and dynamic lookup.


#####3. What does the following function return? Make a prediction before running the code yourself.
```{r}
f <- function(x) {
  f <- function(x) {
    f <- function(x) {
      x ^ 2
    }
    f(x) + 1
  }
  f(x) * 2
}
```

Answer: The function goes down to the lowest level and find x ^ 2, which results in f(x) <- 100. Afterwards, R goes to the command f(x) + 1 and get 100 + 1 = 101, followed by multiplying by two to get 202.

```{r}
f(10)
```



####Exercises - Function arguments

#####1. Clarify the following list of odd function calls:
```{r}
x <- sample(replace = TRUE, 20, x = c(1:10, NA))
y <- runif(min = 0, max = 1, 20)
cor(m = "k", y = y, u = "p", x = x)
```


#####2. What does this function return? Why? Which principle does it illustrate?
```{r}
f1 <- function(x = {y <- 1; 2}, y = 0) {
  x + y
}
f1()
```
Ans: It returns 3. Once the function body is performed, x is set to 2, and y is set to 1. y = 0 is not kept. And then the command x + y is performed. It illustrates lazy evaluation.


#####3. What does this function return? Why? Which principle does it illustrate?
```{r}
f2 <- function(x = z) {
  z <- 100
  x
}
f2()
```
Ans: It returns 100. x is defined in terms of an object that exists only in the function body, which illustrates dynamic lookup and lazy evaluation.


#
####Exercises - Special calls

#####1. Create a list of all the replacement functions found in the base package. Which ones are primitive functions?

Ans:
```{r}
objs <- mget(ls("package:base"), inherits = TRUE)
funs <- Filter(is.function, objs)
repl_funs <- funs[grepl("<-$", names(funs))]
str(repl_funs, max.level = 1, list.len = 6)
prim_repl_funs <- Filter(is.primitive, repl_funs)
str(prim_repl_funs, max.level = 1, list.len = 6)
names(prim_repl_funs)
```


#####2. What are valid names for user-created infix functions?

Ans: All user created infix functions names must start and end with %, e.g., %my_function%.


#####3. Create an infix xor() operator.

Ans:
```{r}
`%xor%` <- function(x, y) {
  (x | y) & !(x & y)
}
```


######4. Create infix versions of the set functions intersect(), union(), and setdiff().

Ans:
```{r}
# intersect()
`%intersect%` = function(x, y) {
    x[x %in% y]
}

# union()
`%union%` = function(x, y) {
    sort(unique(c(x, y)))
}

# setfiff()
`%setdiff%` = function(x, y) {
    x[!(x %in% y)]
}
```


#####5. Create a replacement function that modifies a random location in a vector.

Ans:
```{r}
`random_loc<-` <- function(x, value) {
    id <- sample(1:length(x), 1)
    x[id] <- value
    return(x)
}

(foo <- month.name)
random_loc(foo) <- "Junuary"
foo
```



#
####Exercies - Return values

#####1. How does the chdir parameter of source() compare to in_dir()? Why might you prefer one approach to the other?

Ans:


#####2. What function undoes the action of library()? How do you save and restore the values of options() and par()?

Ans: `detach()` undoes the action of `library()`. 

`options()` and `par()` work the same way as `setwd()`. You can save them while also changing them. So old_par <- par(newpar) will actually save the old options while also setting the new ones:
```{r}
## in a script
old_par <- par(new = TRUE)
par(old_par)

## in a function
foo <- function(...) {
  old_par <- par(new = TRUE)
  on.exit(par(old_par))
  ...
}
```


#####3. Write a function that opens a graphics device, runs the supplied code, and closes the graphics device (always, regardless of whether or not the plotting code worked).

Ans:
```{r}
fn_safe_plot <- function(code, file = 'test.png', ...) {
  png(file = file, ...)
  on.exit(dev.off())
  force(code)
  invisible(NULL)
}

plotter <- function() {
  x <- seq(1:10)
  y <- runif(10)
  plot(x, y)
  on.exit(dev.off())
}
```



#####4. We can use on.exit() to implement a simple version of capture.output().
```{r}
capture.output2 <- function(code) {
  temp <- tempfile()
  on.exit(file.remove(temp), add = TRUE)

  sink(temp)
  on.exit(sink(), add = TRUE)

  force(code)
  readLines(temp)
}
capture.output2(cat("a", "b", "c", sep = "\n"))
```
#####Compare capture.output() to capture.output2(). How do the functions differ? What features have I removed to make the key ideas easier to see? How have I rewritten the key ideas to be easier to understand?

Ans:

