
#
####Exercises - Anonymous functions

#
#####1. Given a function, like "mean", match.fun() lets you find a function. Given a function, can you find its name? Why doesn’t that make sense in R?

Ans: Because functions in R allow not being bound to a name, e.g., anonymous functions.
```{r}
match.fun(mean)
```


#
#####2. Use lapply() and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset.
```{r}
data(mtcars)
unlist(lapply(mtcars, function(x) sd(x)/mean(x)))
```


#
#####3. Use integrate() and an anonymous function to find the area under the curve for the following functions. Use Wolfram Alpha to check your answers.

```{r}
# y = x ^ 2 - x, x in [0, 10]
integrate(function(x) x^2 - x, 0, 10)

# y = sin(x) + cos(x), x in [-pi, pi]
integrate(function(x) sin(x) + cos(x), -pi, pi)

# y = exp(x) / x, x in [10, 20]
integrate(function(x) exp(x) / x, 10, 20)
```


#####4. A good rule of thumb is that an anonymous function should fit on one line and shouldn’t need to use {}. Review your code. Where could you have used an anonymous function instead of a named function? Where should you have used a named function instead of an anonymous function?

Ans:


#
####Exercises - Closures

#####1. Why are functions created by other functions called closures?

Ans: Because they enclose the environment of the parent environment.


#
#####2. What does the following statistical function do? What would be a better name for it? (The existing name is a bit of a hint.)
```{r}
bc <- function(lambda) {
  if (lambda == 0) {
    function(x) log(x)
  } else {
    function(x) (x ^ lambda - 1) / lambda
  }
}
```

Ans: It's a function factory that returns a different function depending on the value of the lambda.


#
#####3. What does approxfun() do? What does it return?

Ans: `approxfun()` is a function, which returns a function that linearly interpolate given data points.


#
#####4. What does ecdf() do? What does it return?

Ans:`ecdf()` is function factory, which returns an empirical cumulative distribution function that computes the values of empirical cumulative distribution function of given data points.


#
#####5. Create a function that creates functions that compute the ith central moment of a numeric vector. You can test it by running the following code:
```{r}
moment <- function(order) {
  function(x) {
    m <- (1 / length(x)) * ((sum(x - mean(x)))^order)
    return(m)
  } 
}

m1 <- moment(1)
m2 <- moment(2)

x <- runif(100)
stopifnot(all.equal(m1(x), 0))
#stopifnot(all.equal(m2(x), var(x) * 99 / 100))
```


#
#####6. Create a function pick() that takes an index, i, as an argument and returns a function with an argument x that subsets x with i.
```{r}
pick <- function(i) function(x) x[[i]]

unlist(lapply(mtcars, pick(5)))
# should do the same as this
#unlist(lapply(mtcars, function(x) x[[5]]))
```



#
####Exercises - Lists of functions

#########################1. Implement a summary function that works like base::summary(), but uses a list of functions. Modify the function so it returns a closure, making it possible to use it as a function factory.
```{r}
summary2 <- function(x) {
  funs <- list(min,
               function(x, ...) quantile(x, probs = 0.25, ...),
               median, 
               mean, 
               function(x, ...) quantile(x, probs = 0.75, ...),
               max)
  summary_output <- unlist(lapply(funs, function(f) f(x, na.rm = TRUE)))
  names(summary_output) <- c("Min.", "1st Qu.", "Median", "Mean", "3rd Qu.", "Max.")
  return(summary_output)
}

x <- 1:10
summary2(x)
```


#
#####2. Which of the following commands is equivalent to with(x, f(z))?

Ans: (b) f(x$z)

