
####Vectors

#####1. What are the six types of atomic vector? How does a list differ from an atomic vector?

Ans: The six types of atomic vectors are : logical, integer, double, character, complex, and raw. List elements don't necessarily have the same type, whereas atomic vector elements have to.


#####2. What makes is.vector() and is.numeric() fundamentally different to is.list() and is.character()?

Ans: `is.vector` and `is.numeric` are general tests, not specific tests for types. However, `is.list` and `is.character` test for exact types.


#####3. Test your knowledge of vector coercion rules by predicting the output of the following uses of c(): 

Ans:

`c(1, FALSE)`:  numeric 1 0

`c("a", 1)`: character "a" "FALSE"

`c(list(1), "a")`: list 1 "a"

`c(TRUE, 1L)`: numeric 1 1


#####4. Why do you need to use unlist() to convert a list to an atomic vector? Why doesn’t as.vector() work?

Ans: `as.vector()` will not coerce to an atomic vector, just leave as a list, while `unlist()` uses the same coercion rules as `c()`.


#####5. Why is 1 == "1" true? Why is -1 < FALSE true? Why is "one" < 2 false?

Ans: Because the logic of 1 equals 1 is true. 
The logic of -1 < FALSE is -1 < 0, which is true. 
"one" < 2 is false because R coerces 2 to "2", and "2" is alphabetically before "one".


#####6. Why is the default missing value, NA, a logical vector? What’s special about logical vectors? (Hint: think about c(FALSE, NA_character_).)

Ans: In the example, using c with a character NA coerces everyting to character. Logical is a the "bottom" of the heirarchy, so it can't drag anything else up to its level.


#
####Attributes and Factors

#####1.An early draft used this code to illustrate structure(): 
```{r}
structure(1:5, comment = "my attribute")
```
#####But when you print that object you don’t see the comment attribute. Why? Is the attribute missing, or is there something else special about it? (Hint: try using help.)

Ans:
Choosing attribute tags that are not comment print fine. `comment` is a special case that is not printed.


#####2. What happens to a factor when you modify its levels? 
```{r}
f1 <- factor(letters) 
levels(f1) <- rev(levels(f1))
```

Ans:
Reversing the factor levels reversed both the vector and its levels.


#####3. What does this code do? How do f2 and f3 differ from f1? 
```{r}
f2 <- rev(factor(letters))
f3 <- factor(letters, levels = rev(letters))
```

Ans: `f2` reverses the vector, but not the levels. `f3` reserves the levels of the vector but not the vector.


#
####Matrices and arrays

#####1.What does `dim()` return when applied to a vector?

Ans: NULL


#####2. If `is.matrix(x)` is TRUE, what will `is.array(x)` return?

Ans: It will return `TRUE` because a matrix is an array.


#####3. How would you describe the following three objects? What makes them different to 1:5? 
```{r}
x1 <- array(1:5, c(1, 1, 5))
x2 <- array(1:5, c(1, 5, 1))
x3 <- array(1:5, c(5, 1, 1))
```

Ans:
`x1` is 1 row by 1 column by 5 deep.
`x2` is 1 row by 5 columns by 1 deep. 
`x3` is 5 rows by 1 column by 1 deep.
They are different from 1:5 because of their dimensionality.


#
####Data Frame

#####1. What attributes does a data frame possess?

Ans: `names`, `row.names`, `class`


#####2. What does `as.matrix()` do when applied to a data frame with columns of different types?

Ans: Coercion into the same type following the coercion rules.


#####3. Can you have a data frame with 0 rows? What about 0 columns?

Ans: Yes, an empty data frame is allowed.


