
#
####Exercises 

```{r}
library(magrittr)
```


#
#####1. Adapt col_summary() so that it only applies to numeric inputs. You might want to start with an is_numeric() function that returns a logical vector that has a TRUE corresponding to each numeric column.
```{r}
(df <- data.frame(a = as.numeric(1:6), b = letters[1:6], c = as.numeric(11:16)))

col_summary <- function(df, FUN, ...) {
  fun_list <- list(
    min1 <- min,
    firstqt <- function(x, ...) quantile(x, probs = 0.25, na.rm = TRUE),
    median <- median,
    mean1 <- mean,
    thirdqt <- function(x, ...) quantile(x, probs = 0.75, na.rm = TRUE),
    max <- max
  )
  df <- df[, sapply(df, is.numeric)]
  summary_output <- as.data.frame(matrix(nrow = 6, ncol = ncol(df)),
                                  row.names = c("Min.   :", "1st Qu.:", "Median :", "Mean   :", "3rd Qu.:", "Max.   :"))
  for (i in seq_along(names(df))) {
    summary_output[, i] <- vapply(fun_list, function(f) f(df[, i], na.rm = TRUE), as.numeric(1))
  }
  colnames(summary_output) <- names(df)
  return(summary_output)
}

col_summary(df)
```


#
#####2. How do sapply() and vapply() differ from col_summary()?

Ans: Both `sapply()` and `vapply()` apply to a column of numeric vector and then return the statstic summary of the vector. However, `col_summary()` can be applied to a data set containing multiple numeric columns and then return the statstic summary of the numeric columns.


